---
title             : "The title"
shorttitle        : "Title"

author: 
  - name          : "First Author"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
    role:         # Contributorship roles (e.g., CRediT, https://casrai.org/credit/)
      - Conceptualization
      - Writing - Original Draft Preparation
      - Writing - Review & Editing
  - name          : "Ernst-August Doelle"
    affiliation   : "1,2"
    role:
      - Writing - Review & Editing

affiliation:
  - id            : "1"
    institution   : "Wilhelm-Wundt-University"
  - id            : "2"
    institution   : "Konstanz Business School"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
 what
 
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib", "ml-references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")

```



*** Ideas for lit review ***

ML vs regression as a function of sample size, number of variables, and maybe other data related properties. 

ML for decision making when promoting.

Using ML to account for covariates (with regression you need to specify covariates, not with ML)

ML reliability when seeking to analyze information in text form quickly, with a different sample other than schools.



*Sajjadiani, S., Sojourner, A. J., Kammeyer-Mueller, J. D., & Mykerezi, E. (2019). Using machine learning to translate applicant work history into predictors of performance and turnover. Journal of Applied Psychology, 104(10), 1207.*
Work experience relevance, tenure in previous positions, applicant attributions of previous turnover as involuntary, applicant attributions of previous turnover to avoiding bad jobs, and applicant attributions of previous turnover to approaching a better job were all used as predictors of performance and turnover using ML algorithms (Naive Bayes Classification). Results matched previous theories of selection, which indicates that ML is a reliable method when seeking to analyze information in text form in a quick and automated way. Idea for dissertation: could do the same thing but with a more general sample instead of schools. 


*Gonzalez, O. (2021). Psychometric and machine learning approaches for diagnostic assessment and tests of individual classification. Psychological Methods, 26(2), 236.*
Comparison between ML methods for test classification vs traditional psychometric methods. Methods that use decision trees naturally seek interactions between items, while methods that use linear models need you to specify if there is an interaction, otherwise they ignore it. 


*Long, Y., Liu, J., Fang, M., Wang, T., & Jiang, W. (2018, May). Prediction of employee promotion based on personal basic features and post features. In Proceedings of the International Conference on Data Processing and Applications (pp. 5-10).*
Data with missing variables for some respondents but not others benefit from ML prediction methods. 







@sajjadiani2019using
@gonzalez2019s
@gonzalez2021psychometric


```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

Center for creative leadership
Bureau of labor statistics
Vendors

# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

## Participants

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses.


# Results

# Discussion


\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
